\documentclass[10pt]{article}
\usepackage{palatino}
\usepackage{fullpage}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fancybox}
\usepackage{framed}

\pagestyle{empty}                       %no page numbers
\thispagestyle{empty}                   %removes first page number
\setlength{\parindent}{0in}

\usepackage{fullpage}
\usepackage[tmargin = 0.5in, bmargin = 1in, hmargin = 1in]{geometry}     %1-inch margins
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}

	\thispagestyle{empty}
	\renewcommand{\headrulewidth}{0.0pt}
	\thispagestyle{fancy}
	\lhead{Name: \underline{\hspace{1.5in}}}
	\chead{MTH 201: Calculus}
	\rhead{\framebox{\textbf{Grade: \ S \quad P}} }
	\lfoot{}
	\cfoot{}
	\rfoot{}


\begin{document}

	\vspace*{0in}

		\begin{center}
			\textbf{Learning Target S12 \\
			Version 3} \\
		\end{center}

\emph{Please place all work in the blank below. If you need more room, use the back of this page.}

\begin{framed}
	\textbf{\textbf{S12:} Estimate a definite integral using a left, right, or midpoint Riemann sum.}
\end{framed}

Estimate the following definite integrals using the indicated Riemann sum. Calculate each Riemann sum out to four decimal places. \textbf{You are allowed to use a calculator on this quiz.}

\begin{enumerate}
    \item $\displaystyle{\int_0^3 (x^3 - 6x) \, dx$ using a right Riemann sum with $n = 3$
    \item $\displaystyle{\int_2^5 \sqrt{x} \, dx$ using a middle Riemann sum with $n = 3$
\end{enumerate}

\vfill


\begin{small}
    \begin{framed}
        	\textbf{Criteria for Satisfactory grade:} The subintervals, $\Delta x$, and terms of the Riemann sum must all be correct. At least one of the two sums must be computed error-free. Minor errors unrelated to the concept are OK for the other one. And, all steps are shown. 
    \end{framed}

\end{small}

\end{document}
